\documentclass[singlesided,
               paper=a4,
               fontsize=10pt
              ]{my-resume}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set geometry
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength\highlightwidth{8cm}
\setlength\headerheight{4cm}            % note that margintop gets added to this value, i.e. the header bar is 5cm
\setlength\marginleft{1cm}
\setlength\marginright{\marginleft}      % needs to be 1.5 times to be actually equal. why?
\setlength\margintop{1cm}
\setlength\marginbottom{1cm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FONTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\RequirePackage{fontspec}
\setmainfont{Carlito}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COLORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\colorlet{highlightbarcolor}{lightgray}
\colorlet{headerbarcolor}{darkgray}

\colorlet{headerfontcolor}{white}
\colorlet{accent}{awesome-red}
\colorlet{heading}{black}
\colorlet{emphasis}{black}
\colorlet{body}{black}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\name{Dmytro Karpus}
\tagline{
    I know React and Vue, and also can use them with  Next.js or Nuxt.js respictivly. Have good knowledge of math,
    so if it is needed can develop math releated things. In addition, I know backend technologies such as Django,
    PHP, Node.js and can write backend using them. Of course, I am ready to learn new technologies or programming 
    languages to use them in new projects. \\
    \\
}

\makeheader

\highlightbar{

    \section{Contact}
    
    \email{dmytro.karpusss@gmail.com}
    \phone{+48 574 704 272}
    \location{Kraków}
    \vspace{0.5em}
    \github{@Dimassss}{https://github.com/Dimassss/IntelligenceAnalyticsTool}
    \linkedin{@pilevoid}{https://www.linkedin.com/in/pilevoid/}
    
    \section{Skills}
    
    \skillsection{Programming}
    \skill{React+Redux/Vue + Vuex}{4}
    \skill{Next.js/Nuxt.js}{4}
    \skill{Java Script/Type Script}{4}
    \skill{Node.js}{4}
    \skill{PHP}{4}
    \skill{Python}{3}
    \skill{HTML/CSS/SCSS}{4}
    
    \vspace{0.5em}
    \skillsection{Operating Systems}
    \skill{Linux}{4}
    \skill{Windows}{5}
    
    \vspace{0.5em}
    \skillsection{Software \& Tools}
    \skill{Git}{4}
    \skill{MySQL / Postgre SQL}{2}
    \skill{Shell}{4}
    
    \vspace{0.5em}
    \skillsection{Languages}
    \skill{Ukrainian}{5}
    \skill{Russian}{5}
    \skill{English}{4}
    \skill{Polish}{4}
    \bigskip

}
\mainbar{
    \section{About Me}
    I started learning programming from school times, because that was interesting for me and still have passion to this. 
    I have less than one year of commercial experience on part-time employment, but now I want work on full-time job as frontend developer.
    As well, I have some projects on git, some of them public, so you can check them. I dont smoke and drink alcohol. I go to gym 3 times a week.
    
    \section[\faMortarBoard]{Education}
    \job{09/2019 - 05/2023}
        {Jagiellonian University, Kraków}
        {Bachelor of Theory Math}
        {}

    \section{General Skills}
    \smallskip % additional skip because tag outlines use up space
    \tag{React JS}
    \tag{Redux}
    \tag{React Router}
    \tag{Ant UI}
    \tag{Next.js}
    \tag{Vue}
    \tag{Vue Router}
    \tag{Vuex}
    \tag{Vuetify}
    \tag{Nuxt.js}
    \tag{Node.js}
    \tag{npm}
    \tag{webpack}
    \tag{git}
    \tag{HTML}
    \tag{CSS3}
    \tag{SCSS}
    \tag{Java Script}
    \tag{Type Script}
    \tag{Postgre SQL}
    \tag{MySQL}
    \tag{PHP}
    \tag{Python}
    \tag{Django}
    \tag{Django REST}
    \tag{OOP}
    \tag{REST API}
    \tag{Linux}
    \tag{Math Analysis}
    \tag{Linear Algebra}
    \tag{Topology}
    \tag{Abstract Algebra}
    \tag{Partial Defferential Equations}
    \tag{Ordinary Differential Equations}
    \tag{Cryptografy}
    \tag{Graph Theory}
    \tag{Complex Analysis}
    \tag{Functional Analysis}
    \tag{Makroekonomy}
    \tag{Probability Theory}
    \tag{Measure theory and integration}
    
}
\makebody
\end{document}